DNSKEY Management

### 2012-12-03 paper/paper.tex
Add more about situation in CH

\paragraph{Certificate Chain} According to a query on
\cite{secspider}, the \verb|ch.| TLD zone is signed and fully
veryfiable from the root zone anchor on downwards. The certificate
chain can hence fully be established and no separate TARs are
required.

\paragraph{Rollover} The validity period of a zone signing key (for
\verb|ch.|) is 37 days \cite{switch10}. For child zones,  DNSSEC and
DNSKEY entries can be enabled and disabled through SWITCH's
web-interface which is able to pull the keys automatically from the
authoritative DNS servers. It is therefore relatively simple to enable
DNSSEC for a \verb|x.ch.| zone, but using the web-interface might be
cumbersome when having to deal with rollovers for a large number of
domains.

>>>>

\paragraph{Certificate Chain} According to a query on
\cite{secspider}, the \verb|ch.| TLD zone is signed and fully
veryfiable from the root zone anchor on downwards. The certificate
chain can hence fully be established and no separate TAR is required.

\paragraph{Penetration} SWITCH states on their website that as of
30. September 2012, 1'734'170 child-zones of \verb|ch.| have been
registered\footnote{\url{https://www.nic.ch/reg/cm/wcm-page/statistics/index.html}}. Upon
inquiry, SWITCH stated that there are around 370 secure delegations
from the \verb|ch.| zone. This is less than $0.02\%$ penetration
rate.

\paragraph{Key Management} The validity period of a zone signing key
(for \verb|ch.|) is 37 days \cite{switch10}. For child zones,  DNSSEC
and DNSKEY entries can be enabled and disabled through SWITCH's 
web-interface which is able to pull the keys automatically from the
authoritative DNS servers. Partners (as Registrars are called in
Switzerland) may also use EPP for key rollover.

Therefore, it is relatively simple to enable DNSSEC for a \verb|x.ch.| 
zone. While using the web-interface is certainly cumbersome when
having to deal with rollovers for a large number of domains, any major
provider may become a SWITCH Partner and can then switch over to EPP
which solves this issue.
